Making (Secure) FETCH Happen: \\ \vspace{2 mm} {\large End-to-End Metadata Security for IMAP}

### 2015-04-28 paper/paper.tex
most of valya's suggestions

\usepackage[normalem]{ulem}
\usepackage{listings}
\lstset{language=Python}

@@

To send an email, the sender's machine send a request to an SMTP server acting on its behalf, which relays it through other SMTP servers until it reaches the recipient's destination server. At that point, the recipient's machine retrieves the email from the server using either POP or IMAP.

\subsubsection{Mail Sending and Transport}
The standard sending and transport protocol is Simple Mail Transfer Protocol (SMTP), first defined in RFC 821 \cite{postel1982rfc} in 1982, and most recently updated in RFC 5321 \cite{klensin2008rfc}. SMTP is an application-layer Internet protocol. In SMTP, a user runs a mail client, or a mail user agent (MUA). This MUA submits mail to a mail server, or a mail submission agent (MSA) on either port 25, 587, or with SSL enabled on 465. The MSA passes the message to a mail transfer agent (MTA), which is often on the same machine as the MSA. The MTA then looks to transfer the message to the recipient's mail exchanger (MX). It does this by looking up the recipient's domain in the Domain name system (DNS). The MTA then sends the email over the Internet to the MX. The MX then sends the email to the recipient's mail delivery agent (MDA). The MDA will either store the message or continue to forward them to another MDA. Upon arriving at their final MDA, the SMTP portion of email delivery is complete.

\label{legacyimap}
\subsubsection{Mail Retrieval, Storage, and Synchronization}
Once a message has arrived at an MDA, the recipient's MUA must retrieve the message. For this, most MUAs use either POP or IMAP. Post Office Protocol (POP) is a simple protocol that enables downloads and deletions, and is most often used when a single client is interested in retrieving mail from an MDA \cite{reynolds1984post}, \cite{myers1996post}. The Internet Message Access Protocol is a more complex protocol that enables multiple clients to be connected to the same mailbox, and has come into more widespread use in recent years \cite{rfc3501}.

@@

\subsection{Non-metadata End-To-End (E2E) Security}
While the standard email protocols are not secure in and of themselves, there have been numerous attempts over the years to provide secure alternatives. Link encryption (sending over SSL/TLS) has been the most widely adopted, but suggestions for messaging with E2E security have been propsed to varying levels of adoption and with a diverse range of feature inclusion \cite{unger2015sok}. These features include synchronicity, deniability and forward/backward secrecy.

@@

\subsubsection{Messaging Apps}
Some of the most usable and widespread E2E solutions are not for email, but for mobile chat. Apple's iMessage application encrypts messages E2E, although their key management system is unknown and may therefore be invisibly compromised \cite{imessage}. Yet their messaging system is not only usable, it is a widely-adopted example of a smooth transition to an updated protocol without problematic updates to the user experience. Signal and TextSecure, from Open Whisper Systems, provide a similar experience, but avoid iMessage's public key infrastructure dependency by using instead a modified version of Off-the-Record Messaging (OTR), which can use solutions to the socialist millionaires problem in place of relying on a previously known public key \cite{borisov2004off}. Crucially, they enable asynchronous messaging by preemptively generating and sending signed key exchange messages \cite{whisper}. They thereby also provide forward secrecy and deniability in an asynchronous setting. Their solution was implemented in the popular messaging application WhatsApp as well \cite{whatsapp}.

@@

\subsubsection{Mailpile and SMTorP}
While anonymous servers abound, mail clients are generally left to the user's preference. Mailpile, though, is a mail client with a goal of integrating security features into the user experience \cite{mailpile}. It integrates key management into its main contact management system, and includes visual indicators (green locks) to denote secure messages in the style of https in browser URL bars. Furthermore, it contains an experimental plugin (SMTorP) that enables users to opportunistically communicate with other users of the plugin, over Tor \cite{smtorp}. SMTorP is semantically similar to SMTP, except that the receiving client runs an SMTP server on the same machine as the mail client, set up as a Tor hidden service. When used in this fashion, an email is sent to the recipient's .onion address instead of a human-chosen address. The authors note that running an SMTP server on a Tor hidden service might be a security liability, since this opens the client to potentially malicious traffic. To address the lack of human-readibility in addresses, the authors consider having users advertise their addresses in the headers of legacy emails that they send, as an invisible upgrade rollout strategy. The protocol also uses hashcash, a proof-of-work algorithm, to defend against spam (bulk commercial unsolicited email).

@@

\label{targetuser}
\section{Target user}

@@

The following graphic displays message timestamps per day of the week and hour of the day, in a Github-style ``punchcard" format \cite{punchcard}.

@@

We can also see message interarrival times \--- that is, the distribution of the length of time between message arrivals and sends. Since this data was taken from the Gmail ``All Mail" mailbox, it includes both received and sent messages, as the set of all messages synchronized to an IMAP server would. Plotted on a linear scale, the ``long tail" distribution is once again evident; since it has an extremely high slope, we show it also on a logarithmic scale for clarity.

@@

\label{architecture}
\section{Architecture and Data Flow}
% Have you defined your overall software architecture? -- describe it in detail and justify your design.

A permissible \project solution must be built to integrate with legacy systems. An MSM MUA will also accept legacy SMTP traffic, and it must appear to the user that all messages, once received, are the same. While the user experience must remain consistent, there are multiple possibilities for architecting a storage system consistent with the storage needs. To architect such a backend, there are several possibilities:

@@

In the \project protocol, a standard IMAP client library is wrapped with a \project module. An MUA then uses the \project module in lieu of a standard IMAP connection agent. The \project module will perform all necessary functions on behalf of the MUA, including encryption, UID translation, and metadata tracking. The IMAP server is unmodified.
% The \project protocol is 
% The core elements of the \project protocol are 
% \begin{enumerate*}[label=(\itshape\arabic*\upshape)]
% \item an \project module used in lieu of a standard IMAP connection agent in an MUA, and
% \item an index file that is stored as a regular message in a legacy IMAP server. \end{enumerate*}
As further described in later sections, \project ensures that metadata is encrypted along with message contents for all messages to be stored on the IMAP server. It also handles the indexing functions, mapping pseudo-mailboxes to the messages they contain. This is a significant departure from the legacy system, where mailbox names and contents were exposed to the IMAP server. As such, it shifts the burden of tracking, updating, and syncing changes to the INDEX from the server to the client. When one client updates the INDEX, the IMAP server will see that a message has changed, and inform its other clients in the standard method.

@@

These changes permit the combination of MSMs and non-MSMs in the same storage system, ensuring an elegant transition to a more secure email. While both types of messages can coexist under \project architecture, the pathways that they traverse to enter the system are distinct. In the next two subsections, we will discuss separately the receipt and insertion methods for messages received via legacy SMTP and for messages received from an alternative metadata-secure transport.

\label{mail-from-secure}
\subsection{Mail From a Secure Source}

When email is received from a metadata-free source (SMTorP, DIME, Pond, etc.), it is stored in a ``cryptoblobs'' mailbox on the IMAP server that the client's \project module has set up. This change is then marked in the INDEX, which is correspondingly updated.

@@

\label{mail-from-insecure}
\subsection{Mail From an Insecure Source}
When an email is received through (legacy) SMTP, it is deleted from the server, its contents and metadata encrypted, and reuploaded to the IMAP server in the same way as an email that was received from a secure source.

  \begin{tikzpicture}[node distance=2.5cm]
  \node (alice) [box] {Alice};
  \node (smtpa) [box, above of=alice] {Alice's legacy \\ SMTP server};
  \node (cloud) [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em, right of=smtpa, xshift=1.3cm] {Network};
  \node (imapb) [box, right of=cloud, xshift=1.4cm] {Bob's legacy \\ IMAP server \\
      \trimbox{0cm 0cm 0cm -.2cm}{
          \begin{tikzpicture}
              \node (index) [box, minimum height=.5cm, outer sep=.2] {INDEX};
          \end{tikzpicture}
      } 
    };

  \node (bob) [box, below of=imapb] {Bob\\
    \trimbox{0cm 0cm 0cm -.2cm}{
    \begin{tikzpicture}
            \node (imaps) [box, minimum height=.5cm, outer sep=.2] {\project module};
        \end{tikzpicture}}};

  \draw [arrow] (alice) -- (smtpa);
  \draw [arrow] (smtpa) -- (cloud);
  \draw [arrow] (cloud) -- (imapb);
  \draw [arrow] (imapb.260) -- (bob.103);
  \draw [arrow] (bob.77) -- (imapb.280);

@@

\label{initialization}
\subsection{Initialization}
Upon logging into an IMAP server, \project attempts to select the CRYPTOBLOBS mailbox. If it succeeds, it assumes that this server has been previously initialized by itself or another client. If there is no CRYPTOBLOBS mailbox, it creates one. It then generates a random salt, appends an initial INDEX with SEQUENCE NUMBER 1 and the salt in the subject line of the INDEX, appends a LOCK, and fetches and loads the INDEX.

\subsection{Command Translations}
The \project module sits between the client and the legacy IMAP module. It translates arguments, processes data, and returns results that give the client a pseudo-view of the contents of the IMAP server informed by the contents of the metadata INDEX. There are four possible pseudo-mailbox classifications. The classification determines the actions that the module takes in response to each command. A PSEUDO mailbox is not mirrored in the IMAP server; it exists only in the INDEX and is thus only known to clients following the \project protocol. A HYBRID mailbox exists both in the IMAP server and in the INDEX. This is a mailbox such as INBOX, which must also be known the IMAP server as a location for the delivery of incoming messages. A PSEUDO/HIDDEN pseudo-mailbox neither exists in the IMAP server nor is known to the client. It is for use only by the \project module. The FAKE\_MESSAGES pseudo-mailbox used by the scheduler is an example of this type of pseudo-mailbox. An ACTUAL/HIDDEN mailbox is known to the IMAP server but not to the \project client. The CRYPTOBLOBS mailbox, the mailbox in which all encrypted messages are stored on the IMAP server, is an example of this type of mailbox.

\label{select}
\subsubsection{SELECT} In a view of the system enforced by the Python wrapper for an imap connection, imaplib, when a SELECT command is passed to the IMAP module, the state of the IMAP server changes to record that a particular client connection has selected a mailbox, and returns a count of the number of messages in that mailbox. When the \project module receives a SELECT command, it saves the requested mailbox to an instance variable. If the requested mailbox is a HYBRID mailbox, it passes the count onto the IMAP server. For both PSEUDO and HYBRID mailboxs, it then calculates the number of messages in the mailbox based on the INDEX, and adds that to either the returned value or 0. If a HIDDEN mailbox is requested, a NO response is returned. Note that the counting functionality is implemented by the EXISTS untagged request as described in Section~\ref{exists} - the SELECT command elicits the EXISTS server response, whose value is used for the return value of the Python function.

@@

\label{exists}
\subsubsection{EXISTS} EXISTS is functionally equivalent to the return value of SELECT. The technical definition is the number of messages in the mailbox.

@@

\label{uid-translation}
\subsection{UID Storage and Lookup}
While all encrypted messages are stored on the IMAP server in the CRYPTOBLOBS mailbox, the client's view should allow for a more complex representation of which messages are stored in which mailboxes. At a minimum, we would like to support an INBOX mailbox for messages that are received at the IMAP server, and an SMTorP or Pond pseudo-mailboxes for messages that are received at the client via a metadata-secure transport mechanism. Thus, each message needs an associated UID for its pseudo-mailbox, or the mailbox that the message is in as it appear to the client. But it also has an actual UID, or the UID inside the CRYPTOBLOBS mailbox. This UID is assigned by the IMAP server when \project APPENDs a message to a mailbox on the server. The APPEND command does not, however, return the assigned UID. Therefore we need a separate mechanism for associating a message's pseudo-UID with its actual UID.

@@

\label{processing}
\subsection{Processing Messages Received at IMAP Server}
When a message is received at the IMAP Server as in Section~\ref{mail-from-insecure}, \project processes the message so it is equivalent to messages that arrived at the client machine from a secure source. To process a message, \project fetches the body of the message, adds it to CRYPTOBLOBS, and deletes it from the INBOX. Note that without any mixing here or during scheduled message exchanges, it is trivial for an IMAP server to keep track of which message in CRYPTOBLOBS corresponds to which message that was received in the INBOX, because the server will see that a message was added to CRYPTOBLOBS and deleted from INBOX at about the same time. The process used for adding the message to CRYPTOBLOBS is equivalent to the process for adding a message from an insecure source, or for adding a scheduled fake message. The process for adding a message to a pseudo-mailbox involves several steps. We update the INDEX, possibly adding the mailbox to the INDEX if it is the first time we have seen it. We generate a UNIQUE SUBJECT number. If the mailbox is of type PSEUDO, we compute the pseudo-UID for the message. As per RFC 3501, the UID assigned is strictly greater than any UID that has been previously assigned in the mailbox. We store in the INDEX the state of the NEXT UID to assign.

@@

Because of this delete/upload lock acquisition mechanism, the IMAP server may sometimes be in a state where the LOCK message does not exist but no client holds the lock, such as if a client crashes or closes down while holding the lock. Optimally, this would not happen, and the lock would be released before closing, but the existing library does not require a method to be called on close, so we cannot rely on a client to release a lock before quitting. Thus, \project includes a mechanism for detecting this inconsistent state and recovering from it by acquiring a lock even if the LOCK message does not exist in the CRYPTOBLOBS mailbox.

@@

\label{encryption}
\subsection{Encryption}

@@

\label{rollback}
\subsection{Rollback Detection}
While we cannot rely on the IMAP server for availability, we can detect and decline to accept rollback of any part of the system. In a rollback attack, an adversary in control of the server can partially or completely snapshot the files on the server at any given time, then later replace a file with that name with the old contents. So, if the server took a snapshot of one version of the INDEX, then a client changes the INDEX to reflect deletion of a message, the server could later replace the current INDEX with the previous one, making it appear as though the message had not been deleted. This would be particularly problematic if a unique subject is reused, which could cause a client to receive a different message for that subject than they should have seen.

@@

Fundamentally, scheduling means that \project performs an action at a predetermined time tick. To better reason about the leakage of information, \project contains a separate scheduler module (shown above) that is informed when a message arrives or is marked for deletion. It thus can reason about the expansion rate of the server. At the scheduled time tick, \project will ask the scheduler what its next action should be. This can be one of three types: UP, DOWN, or NONE. UP means that the server will grow in size by one message, DOWN means that it will shrink by one message, and NONE means that the total server size will remain constant. The trit that it outputs is based on its metadata protection policy, determined in conjunction with the \project module. We separate this functionality into the scheduler because it precisely mirrors the information that the server will receive: whether a message has been pushed up, pulled down, or neither. Thus, the server can gain no more than one trit of data on every time tick.

@@

\label{best-metadata}
\subsection{Strategies}

@@

ORAM makes assumptions that we could perhaps consider relaxing. First, ORAM assumes constant, fixed-size blocks of memory. Messages in a mail server need not be constant size, although any solution that involves mixing will require elements of the mix to all be of the same size. Second, a primary goal of ORAM is to hide correlated memory locations. If messages are not decomposed into fixed-size chunks and all saved into the same pseudo-mailbox, then an individual message is not correlated with any other message. Note that mixing will generally require chunking of messages, and we wish to support multiple pseudo-mailboxes, but locations are not as inherently correlated in all cases as they are when a program is executing on memory locations. Third, mailboxes do not allow store operations in the sense of RAM; IMAP only supports appending to mailboxes. Even under these relaxations, most solutions that do not implement an ORAM-adherent technique will trade off either functionality or security.

@@

If we wish the growth rate of the server to precisely match the rate of messages to be pushed, we must perform many mixing operations. Intuitively, this is because to grow with the actual rate, each fake message that was in an UP operation must appear in a DOWN operation. Mathematically, assume that the mailbox is seeded with $k-1$ fake messages. Consider again messages R and F, and call MIX NUMBER $m$. This time, R and F were each one of $m + 1$ messages pushed to the server, with R pushed into set A and F pushed into set B. Assume no overlap between A and B, since $m<<n$, the total number of messages. This case is similar to the case of no extraneous growth without mixing assessed above, since we are extremely unlikely to have chosen a message in set B were one of them not fake. More precisely, we have at least a $1/k$ probability of choosing a messaging from set B. For choosing at least one message from set A, though, we have a probability equivalent to $1-$ the probability of choosing 0 messages from set A. This is equivalent to choosing all $m$ messages from the $n-m$ messages not in set A, which there are ${{n-m}\choose m}$ ways to do. This gives a probability of choosing at least one message of the $m$ chosen messages from set A of $1-\frac{{{n-m}\choose m}}{{n \choose m}}$.

>>>>

\usepackage[normalem]{ulem}
\usepackage{listings}
\lstset{language=Python}
\usepackage{multirow}

@@

To send an email, the sender's machine sends a request to an SMTP server acting on its behalf, which relays it through other SMTP servers until it reaches the recipient's destination server. At that point, the recipient's machine retrieves the email from the server using either POP or IMAP.

\subsubsection{Mail Sending and Transport}
The standard sending and transport protocol is Simple Mail Transfer Protocol (SMTP), first defined in RFC 821 \cite{postel1982rfc} in 1982, and most recently updated in RFC 5321 \cite{klensin2008rfc}. SMTP is an application-layer Internet protocol. In SMTP, a user runs a mail client, or a mail user agent (MUA). This MUA submits mail to a mail server, or a mail submission agent (MSA) on either port 25, 587, or with SSL enabled on 465. The MSA passes the message to a mail transfer agent (MTA), which is often on the same machine as the MSA. The MTA then looks to transfer the message to the recipient's mail exchanger (MX). It does this by looking up the recipient's domain in the Domain Name System (DNS). The MTA then sends the email over the Internet to the MX. The MX then sends the email to the recipient's mail delivery agent (MDA). The MDA will either store the message or continue to forward them to another MDA. Upon arriving at their final MDA, the SMTP portion of email delivery is complete.

\subsubsection{Mail Retrieval, Storage, and Synchronization}
\label{legacyimap}
Once a message has arrived at an MDA, the recipient's MUA must retrieve the message. For this, most MUAs use either POP or IMAP. Post Office Protocol (POP) is a simple protocol that enables downloads and deletions, and is most often used when a single client is interested in retrieving mail from an MDA \cite{reynolds1984post}, \cite{myers1996post}. The Internet Message Access Protocol is a more complex protocol that enables multiple clients to be connected to the same mailbox, and has come into more widespread use in recent years \cite{rfc3501}.

@@

\subsection{Non-metadata End-To-End (E2E) Security}
While the standard email protocols are not secure in and of themselves, there have been numerous attempts over the years to provide secure alternatives. Link encryption (sending over SSL/TLS) has been the most widely adopted, but suggestions for messaging with E2E security have been proposed to varying levels of adoption and with a diverse range of feature inclusion \cite{unger2015sok}. These features include synchronicity, deniability and forward/backward secrecy.

@@

\subsubsection{Messaging Apps}
Some of the most usable and widespread E2E solutions are not for email, but for mobile chat. Apple's iMessage application encrypts messages E2E, although their key management system is unknown and may therefore be invisibly compromised \cite{imessage}. Yet their messaging system is not only usable, it is a widely-adopted example of a smooth transition to an updated protocol without problematic updates to the user experience. Signal and TextSecure, from Open Whisper Systems, provide a similar experience, but avoid iMessage's public key infrastructure dependency by using instead a modified version of Off-the-Record Messaging (OTR), which can use solutions to the socialist millionaires problem in place of relying on a previously known public key \cite{borisov2004off}. The socialist millionaires problem is a zero-knowledge construction where multiple parties would like to test private values for equality without revealing any information to the other party other than the result of the test. Crucially, Signal and TextSecure enable asynchronous messaging by preemptively generating and sending signed key exchange messages \cite{whisper}. They thereby also provide forward secrecy and deniability in an asynchronous setting. The technology used to implement their solution was implemented in the popular messaging application WhatsApp as well \cite{whatsapp}.

@@

\subsubsection{Mailpile and SMTorP}
While anonymous servers abound, mail clients are generally left to the user's preference. Mailpile, though, is a mail client with a goal of integrating security features into the user experience \cite{mailpile}. It integrates key management into its main contact management system, and includes visual indicators (green locks) to denote secure messages in the style of https in browser URL bars. Furthermore, it contains an experimental plugin (SMTorP) that enables users to opportunistically communicate with other users of the plugin, over Tor \cite{smtorp}. SMTorP is semantically similar to SMTP, except that the receiving client runs an SMTP server on the same machine as the mail client, set up as a Tor hidden service. When used in this fashion, an email is sent to the recipient's .onion address instead of a human-chosen address. The authors note that running an SMTP server on a Tor hidden service might be a security liability, since this opens the client to potentially malicious traffic. Additionally, the alphanumeric string preceding the .onion address is not human-memorable. To address the lack of human-memorability in addresses, the authors consider having users advertise their addresses in the headers of legacy emails that they send, as an invisible upgrade rollout strategy. Clients could then advertise their upgraded status through these headers, invisibly switching to the new protocol when both communicating parties have received the .onion address associated with the legacy email address. The protocol also uses hashcash, a proof-of-work algorithm, to defend against spam (bulk commercial unsolicited email).

@@

\section{Target user}
\label{targetuser}

@@

The following graphic displays message timestamps per day of the week and hour of the day, in a Github-style ``punchcard" format \cite{punchcard}. In this graphic, day-time combinations that receive more messages are shaded darker, and with larger circles.

@@

We can also see message interarrival times \--- that is, the distribution of the length of time between message arrivals and sends. Since this data was taken from the Gmail ``All Mail" mailbox, it includes both received and sent messages, as the set of all messages synchronized to an IMAP server would. Plotted on a linear scale, the ``long tail" distribution is once again evident; since it has an extremely high slope, we show it also on a logarithmic scale for clarity. The vertical axis shows the total number of messages with inter-message arrival time less than or equal to the corresponding value on the horizontal axis.

@@

\section{Architecture and Data Flow}
\label{architecture}

% Have you defined your overall software architecture? -- describe it in detail and justify your design.

A permissible \project solution must be built to integrate with legacy systems. A metadata-secure MUA will also accept legacy SMTP traffic, and it must appear to the user that all messages, once received, are the same. While the user experience must remain consistent, there are multiple possibilities for architecting a storage system consistent with the storage needs. To architect such a backend, there are several possibilities:

@@

In the \project protocol, a standard IMAP client library is wrapped with a \project module. An MUA then uses the \project module in lieu of a standard IMAP connection agent. The \project module will perform all necessary functions on behalf of the MUA, including encryption, UID translation, and metadata tracking. The IMAP server is unmodified.
% The \project protocol is 
% The core elements of the \project protocol are 
% \begin{enumerate*}[label=(\itshape\arabic*\upshape)]
% \item an \project module used in lieu of a standard IMAP connection agent in an MUA, and
% \item an index file that is stored as a regular message in a legacy IMAP server. \end{enumerate*}
As further described in later sections, \project ensures that metadata is encrypted along with message contents for all messages to be stored on the IMAP server. It also handles the indexing functions, mapping pseudo-mailboxes to the messages they contain. This is a significant departure from the legacy system, where mailbox names and contents were exposed to the IMAP server. As such, it shifts the burden of tracking, updating, and syncing changes to the message metadata store (the INDEX) from the server to the client. When one client updates the INDEX, the IMAP server will see that a message has changed, and inform its other clients in the standard method.

@@

These changes permit the combination of metadata-secure messages and non-metadata-secure messages in the same storage system, ensuring an elegant transition to a more secure email. While both types of messages can coexist under \project architecture, the pathways that they traverse to enter the system are distinct. In the next two subsections, we will discuss separately the receipt and insertion methods for messages received via legacy SMTP and for messages received from an alternative metadata-secure transport.

\subsection{Mail From a Secure Source}
\label{mail-from-secure}

When email is received from a metadata-free source (SMTorP, DIME, Pond, etc.), it is stored in a ``CRYPTOBLOBS'' mailbox on the IMAP server that the client's \project module has set up. This change is then marked in the INDEX, which is correspondingly updated.

@@

\subsection{Mail From an Insecure Source}
\label{mail-from-insecure}

When an email is received through (legacy) SMTP, it is deleted from the server, its contents and metadata encrypted, and reuploaded to the IMAP server in the same way as an email that was received from a secure source.

  \begin{tikzpicture}[node distance=2.5cm]
  \node (alice) [box] {Alice};
  \node (smtpa) [box, above of=alice] {Alice's legacy \\ SMTP server};
  \node (cloud) [cloud, draw,cloud puffs=10,cloud puff arc=120, aspect=2, inner ysep=1em, right of=smtpa, xshift=1.3cm] {Network};
  \node (imapb) [box, minimum width = 4cm, right of=cloud, xshift=1.4cm] {Bob's legacy \\ IMAP server \\
      \trimbox{0cm 0cm 0cm -.2cm}{
          \begin{tikzpicture}
              \node (index) [box, minimum height=.5cm, outer sep=.2] {INDEX};
          \end{tikzpicture}
      } 
    };

  \node (bob) [box, minimum width = 4cm, below of=imapb] {Bob\\
    \trimbox{0cm 0cm 0cm -.2cm}{
    \begin{tikzpicture}
            \node (imaps) [box, minimum height=.5cm, outer sep=.2] {\project module};
        \end{tikzpicture}}};

  \draw [arrow] (alice) -- (smtpa);
  \draw [arrow] (smtpa) -- (cloud);
  \draw [arrow] (cloud) -- (imapb);
  \draw [arrow] (imapb.260) -- (bob.106);
  \draw [arrow] (bob.74) -- (imapb.280);

@@

\subsection{Initialization}
\label{initialization}

Upon logging into an IMAP server, \project attempts to select the CRYPTOBLOBS mailbox. If it succeeds, it assumes that this server has been previously initialized by itself or another client. If there is no CRYPTOBLOBS mailbox, it creates one. It then generates a random salt, appends an initial INDEX with SEQUENCE NUMBER 1 and the salt in the subject line of the INDEX, appends a LOCK, and fetches and loads the INDEX.

\subsection{Command Translations}
In the IMAP server/client model, the client sends commands to the server, and the server responds based on its state and contents. These commands are the primary form of synchronizing data between the server and its clients.The \project module sits between the client and the legacy IMAP module. It translates arguments, processes data, and returns results that give the client a pseudo-view of the contents of the IMAP server informed by the contents of the metadata INDEX.

We can classify mailboxes by two features: their visibility to the server, and their visibility to the client. When the client's view of the mailbox is used, it is referred to as a pseudo-mailbox. There are four possible mailbox classifications. The classification determines the actions that the module takes in response to each command. A PSEUDO mailbox is not mirrored in the IMAP server; it exists only in the INDEX and is thus only known to clients following the \project protocol. SMTorP is an example of a PSEUDO mailbox. A HYBRID mailbox exists both in the IMAP server and in the INDEX. This is a mailbox such as INBOX, which must also be known the IMAP server as a location for the delivery of incoming messages. A PSEUDO/HIDDEN pseudo-mailbox neither exists in the IMAP server nor is known to the client. It is for use only by the \project module. The FAKE\_MESSAGES pseudo-mailbox used by the scheduler is an example of this type of pseudo-mailbox. An ACTUAL/HIDDEN mailbox is known to the IMAP server but not to the \project client. The CRYPTOBLOBS mailbox, the mailbox in which all encrypted messages are stored on the IMAP server, is an example of this type of mailbox. These classifications are shown in the table below.

\begin{tabular}{ rr|c|c| }

 &\multicolumn{1}{r}{} & \multicolumn{2}{c}{Visible to Client?} \\

&\multicolumn{1}{r}{}
 &  \multicolumn{1}{c}{Yes}
 & \multicolumn{1}{c}{No} \\
\cline{3-4}
\multirow{2}{*}{Visible to Server?} & Yes & INBOX & CRYPTOBLOBS \\
\cline{3-4}
& No & SMTorP & FAKE\_MESSAGES \\
\cline{3-4}
\end{tabular}

\subsubsection{SELECT}
\label{select}

In a view of the system enforced by the Python wrapper for an IMAP connection, imaplib, when a SELECT command is passed to the IMAP module, the state of the IMAP server changes to record that a particular client connection has selected a mailbox, and returns a count of the number of messages in that mailbox. When the \project module receives a SELECT command, it saves the requested mailbox to an instance variable. If the requested mailbox is a HYBRID mailbox, it passes the count onto the IMAP server. For both PSEUDO and HYBRID mailboxs, it then calculates the number of messages in the mailbox based on the INDEX, and adds that to either the returned value or 0. If a HIDDEN mailbox is requested, a NO response is returned. Note that the counting functionality is implemented by the EXISTS untagged request as further described in Section~\ref{exists} - the SELECT command additionally elicits the EXISTS server response, whose value is used for the return value of the Python function.

@@

\subsubsection{EXISTS}
\label{exists}

EXISTS is functionally equivalent to the return value of SELECT. The technical definition is the number of messages in the mailbox.

@@

\subsection{UID Storage and Lookup}
\label{uid-translation}

While all encrypted messages are stored on the IMAP server in the CRYPTOBLOBS mailbox, the client's view should allow for a more complex representation of which messages are stored in which mailboxes. At a minimum, we would like to support an INBOX mailbox for messages that are received at the IMAP server, and an SMTorP or Pond pseudo-mailbox for messages that are received at the client via a metadata-secure transport mechanism. Thus, each message needs an associated UID for its pseudo-mailbox, or the mailbox that the message is in as it appear to the client. But it also has an actual UID, or the UID inside the CRYPTOBLOBS mailbox (the server-view mailbox that stores all messages processed by \projectnospace). This UID is assigned by the IMAP server when \project APPENDs a message to a mailbox on the server. The APPEND command does not, however, return the assigned UID. Therefore we need a separate mechanism for associating a message's pseudo-UID with its actual UID.

@@

\subsection{Processing Messages Received at IMAP Server}
\label{processing}

When a message is received at the IMAP Server as in Section~\ref{mail-from-insecure}, \project processes the message so it bears surface equivalence to messages that arrived at the client machine from a secure source. Note that full equivalence can only be achieved by also including mixing steps either here or during scheduled message exchanges. Without them, it is trivial for an IMAP server to keep track of which message in CRYPTOBLOBS corresponds to which message that was received in the INBOX, because the server will see that a message was added to CRYPTOBLOBS and deleted from INBOX at about the same time.

To process a message, \project fetches the body of the message, adds it to CRYPTOBLOBS, and deletes it from the INBOX. The process used for adding the message to CRYPTOBLOBS is equivalent to the process for adding a message from an insecure source, or for adding a scheduled fake message. The process for adding a message to a pseudo-mailbox involves several steps. We update the INDEX, possibly adding the mailbox to the INDEX if it is the first time we have seen it. We generate a UNIQUE SUBJECT number. If the mailbox is of type PSEUDO, we compute the pseudo-UID for the message. As per RFC 3501, the UID assigned is strictly greater than any UID that has been previously assigned in the mailbox. We store in the INDEX the state of the NEXT UID to assign.

@@

Because of this delete/upload lock acquisition mechanism, the IMAP server may sometimes be in a state where the LOCK message does not exist but no client holds the lock, such as if a client crashes or closes down while holding the lock. Optimally, this would not happen, and the lock would be released before closing. Unfortunately, the existing library allows its client to close its socket directly, rather than through a specified method at the library level, so we cannot rely on a client to release a lock before quitting. Thus, \project includes a mechanism for detecting this inconsistent state and recovering from it by acquiring a lock even if the LOCK message does not exist in the CRYPTOBLOBS mailbox.

@@

\subsection{Encryption}
\label{encryption}

@@

\subsection{Rollback Detection}
\label{rollback}

While we cannot rely on the IMAP server for availability, we can detect and decline to accept rollback of any part of the system. In a rollback attack, an adversary in control of the server can partially or completely snapshot the files on the server at any given time, then later replace a file with that name with the old contents. So, if the server took a snapshot of one version of the INDEX, then a client changes the INDEX to reflect deletion of a message, the server could later replace the current INDEX with the previous one, making it appear as though the message had not been deleted. This would be particularly problematic if a unique subject is reused, which could cause a client to receive a different message for that subject than they should have seen.

@@

Fundamentally, scheduling means that \project performs an action at a predetermined time tick. To better reason about the leakage of information, \project contains a separate scheduler module (shown above) that is informed when a message arrives or is marked for deletion. It thus can reason about the expansion rate of the server. At the scheduled time tick, \project will ask the scheduler what its next action should be. This can be one of three types: UP, DOWN, or NONE. UP means that the server will grow in size by one message, DOWN means that it will shrink by one message, and NONE means that the total server size will remain constant. The ternary digit (trit) that it outputs is based on its metadata protection policy, determined in conjunction with the \project module. We separate this functionality into the scheduler because it precisely mirrors the information that the server will receive: whether a message has been pushed up, pulled down, or neither. Thus, the server can gain no more than one trit of data on every time tick.

@@

\subsection{Strategies}
\label{best-metadata}

@@

ORAM makes assumptions that we could perhaps consider relaxing. First, ORAM assumes constant, fixed-size blocks of memory. Messages in a mail server need not be constant size, although any solution that involves mixing will require elements of the mix to all be of the same size. Second, a primary goal of ORAM is to hide correlated memory locations; that is, memory locations that are often accessed together and might therefore reveal information about the structure of the program or the data. We could theoretically restrict ourselves from the full scope of desirable actions, such as by choosing not to decompose messages into fixed-size chunks and saving all messages into the same pseudo-mailbox. Were we to do so, then an individual message will not be inherently correlated with any other message. Note that mixing will generally require chunking of messages, and we wish to support multiple pseudo-mailboxes, but locations are not as inherently correlated in all cases as they are when a program is executing on memory locations. Third, mailboxes do not allow store operations in the sense of RAM; IMAP only supports appending to mailboxes. Even under these relaxations, most solutions that do not implement an ORAM-adherent technique will trade off either functionality or security.

@@

If we wish the growth rate of the server to precisely match the rate of messages to be pushed, we must perform many mixing operations. Intuitively, this is because to grow with the actual rate, each fake message that was in an UP operation (a scheduled exchange with the server where one more message is sent to the server than is deleted from the server) must appear in a DOWN operation (a scheduled exchange with the server where one fewer message is sent to the server than is deleted from the server). Mathematically, assume that the mailbox is seeded with $k-1$ fake messages. Consider again messages R and F, and call MIX NUMBER $m$. This time, R and F were each one of $m + 1$ messages pushed to the server, with R pushed into set A and F pushed into set B. Assume no overlap between A and B, since $m<<n$, the total number of messages. This case is similar to the case of no extraneous growth without mixing assessed above, since we are extremely unlikely to have selected a message in set B for inclusion in the mix were one of them not fake. More precisely, we have at least a $1/k$ probability of choosing a messaging from set B. For choosing at least one message from set A, though, we have a probability equivalent to $1-$ the probability of choosing 0 messages from set A. This is equivalent to choosing all $m$ messages from the $n-m$ messages not in set A, which there are ${{n-m}\choose m}$ ways to do. This gives a probability of choosing at least one message of the $m$ chosen messages from set A of $1-\frac{{{n-m}\choose m}}{{n \choose m}}$.

For a reasonable estimation, assume $n=5000$ and $m=10$, which gives a probability of choosing from set A of slightly under 0.02. Then, $k$ must be at least 50 to give equivalent probabilities for choosing from sets A and B. But this analysis only applies if the adversary does not know which of the messages are the fake $k$ at every time step. So, how many mixing operations do we require to completely mix all $n$ messages? If we are selecting at random, this is the expected number of operations required to select all $n$ messages in batches of $m$, which is a variation on the coupon collector problem. It is not precisely the coupon collector problem, since we are selecting $m$ at a time, and therefore one batch cannot contain duplicates of the same message, so there is a slightly higher probability of selecting a new one for later messages in a batch. Thus, we can place a lower bound on the number of mixing operations required to select $n$ messages at $E(n) = n \ln (n) / m$. Using our estimates of $5000$ and 10, this is over 4000 mixing operations. We must pull down and push up a total of $2m$ messages for each operation, so that is $2n\ln (n)$ messages that must be transferred to entirely mix the mailbox regardless of $m$. This is unreasonable to do on a regular basis.
